Multiset-Trie Data Structure

### 2023-03-20 tex/algorithms-2122309-proof.tex
removed higlighting, ZIP

\begin{figure}[H]
	\subcaptionbox{\centering  \label{fig:e1m1}}{\includegraphics[width=.485\textwidth]{exp1-m1.pdf}}
	\subcaptionbox{\centering \label{fig:e1m2}}{\includegraphics[width=.485\textwidth]{exp1-m2.pdf}}
	\caption{\hl{Existence} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 functions of Experiment 1. (\textbf{a}) submsetExistence; %MDPI: We moved the subfigure explanations into the figure caption. Please confirm. The following are same. %RES We confirm.
 (\textbf{b}) supermsetExistence.  \label{fig:4}}
\end{figure}

@@

\subcaptionbox{\centering 
\label{fig:e1m3}}{\includegraphics[width=.485\textwidth]{exp1-m3.pdf}
}
\subcaptionbox{\centering 
\label{fig:e1m4}}{\includegraphics[width=.485\textwidth]{exp1-m4.pdf}
}
\caption{\hl{Exhaustive} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000". please check all figures.
 functions of Experiment 1. (\textbf{a}) \hl{getAllSubmsets}; (\textbf{b}) \hl{getAllSupermsets}.\label{fig:5}}
\end{figure}

@@

\begin{figure}[H]
\subcaptionbox{\centering
}{\includegraphics[width=.485\textwidth]{exp2-m1.pdf}}
\subcaptionbox{\centering
\label{fig:e2m2}}{\includegraphics[width=.485\textwidth]{exp2-m2.pdf}}
\caption{Existence functions in Experiment 2. (\textbf{a}) \hl{submsetExistence}; (\textbf{b}) \hl{supermsetExistence}.\label{fig:e2m1}}
\end{figure}

@@

\begin{figure}[H]
\subcaptionbox{\centering \hl{Experiment} %MDPI Please move sub-caption to Caption.
2, getAllSubmsets function.
}{\includegraphics[width=.485\textwidth]{exp2-m3.pdf}}
\subcaptionbox{\centering \hl{Experiment} 2, getAllSupermsets function.
\label{fig:e2m4}}{\includegraphics[width=.485\textwidth]{exp2-m4.pdf}}
\caption{Exhaustive functions in Experiment 2.\label{fig:e2m3}}
\end{figure}

@@

\begin{table}[H]
\caption{Configuration %MDPI: We removed the vertical lines. Please confirm. %RES We confirm.
 of $\sigma$ and $n$ in benchmark.}
\label{t:benchmark}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CC}
\toprule
\boldmath$\sigma$ & \boldmath$n$ \\
\midrule
5		& 1\\
%\hline
30	& 1 \\
%\hline
5		& 3 \\
%\hline
15	& 3 \\
%\hline
30	& 3 \\
%\hline
10	& 10 \\
\bottomrule
\end{tabularx}
\end{table}

>>>>

\begin{figure}[H]
	\subcaptionbox{\centering  \label{fig:e1m1}}{\includegraphics[width=.485\textwidth]{exp1-m1.pdf}}
	\subcaptionbox{\centering \label{fig:e1m2}}{\includegraphics[width=.485\textwidth]{exp1-m2.pdf}}
	\caption{{Existence} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 functions of Experiment 1. (\textbf{a}) submsetExistence; %MDPI: We moved the subfigure explanations into the figure caption. Please confirm. The following are same. %RES We confirm.
 (\textbf{b}) supermsetExistence.  \label{fig:4}}
\end{figure}

@@

\subcaptionbox{\centering 
\label{fig:e1m3}}{\includegraphics[width=.485\textwidth]{exp1-m3.pdf}
}
\subcaptionbox{\centering 
\label{fig:e1m4}}{\includegraphics[width=.485\textwidth]{exp1-m4.pdf}
}
\caption{{Exhaustive} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000". please check all figures.
 functions of Experiment 1. (\textbf{a}) {getAllSubmsets}; (\textbf{b}) {getAllSupermsets}.\label{fig:5}}
\end{figure}

@@

\begin{figure}[H]
\subcaptionbox{\centering
}{\includegraphics[width=.485\textwidth]{exp2-m1.pdf}}
\subcaptionbox{\centering
\label{fig:e2m2}}{\includegraphics[width=.485\textwidth]{exp2-m2.pdf}}
\caption{Existence functions in Experiment 2. (\textbf{a}) {submsetExistence}; (\textbf{b}) {supermsetExistence}.\label{fig:e2m1}}
\end{figure}

@@

\begin{figure}[H]
\subcaptionbox{\centering {Experiment} %MDPI Please move sub-caption to Caption.
2, getAllSubmsets function.
}{\includegraphics[width=.485\textwidth]{exp2-m3.pdf}}
\subcaptionbox{\centering {Experiment} 2, getAllSupermsets function.
\label{fig:e2m4}}{\includegraphics[width=.485\textwidth]{exp2-m4.pdf}}
\caption{Exhaustive functions in Experiment 2.\label{fig:e2m3}}
\end{figure}

@@

\begin{table}[H]
\caption{Configuration %MDPI: We removed the vertical lines. Please confirm. %RES We confirm.
 of $\sigma$ and $n$ in benchmark.}
\label{t:benchmark}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CC}
\toprule
\boldmath$\sigma$ & \boldmath$n$ \\
\midrule
5		& 1\\
30	& 1 \\
5		& 3 \\
15	& 3 \\
30	& 3 \\
10	& 10 \\
\bottomrule
\end{tabularx}
\end{table}
